COVID-19 Closures Impact Restaurant Revenue and Employment Unequally

### 2021-02-24 outputs/paper/paper.Rmd

---
title: "COVID-19 Closures Impact Restaurant Revenue and Employment Unequally"
author: "Lorena Almaraz De La Garza, Amy Farrow, and Kumalasari Sondjaja"
date: "September 20th, 2021"
output:
  bookdown::pdf_document2:
    toc: yes
subtitle: "A random controlled trial to identify the impact of mandatory partial closures on Ontario restaurants"
abstract: "This report covers an experiment conducted by Petit Poll to test the impact of COVID-19 closures on Ontario restaurants. A randomized controlled trial was conducted and surveys were used to collect results. The data show that restaurant revenue and employee counts were negatively impacted by a mandatory two-week partial closure, and dine-in restaurants and restaurants owned by visible minorites were more negatively impacted. These results suggest that if more closures are necessary, Ontario should support restaurant owners by offering support for take-out services and minority-owned businesses."
thanks: 'Code and data are available at: [github.com/amycfarrow/ontariorestaurantclosuresexperiment](https://github.com/amycfarrow/ontariorestaurantclosuresexperiment).'
bibliography: references.bib
---

@@

The target population for this study was all restaurants in Ontario. Because restaurant inspection is carried out by different authorities across the province, a list of Ontario local health authorities (LHAs) was collected. These LHAs were the primary sampling units, forming the primary sampling frame, or list of units of interest from which to draw a sample. Using census data from 2016, the primary sampling frame was stratified into small LHAs (population of less than 150,000), medium LHAs (population of 150,000 to 400,000), and large LHAs (population of more than 400,000). Each strata contained the same number of LHAs. From each stratum, two LHAs were randomly sampled to participate in the treatment, and two LHAs were randomly selected to participate in the control. This primary sample is shown in Table \@ref(tab:treatmentcontrolgroups).

@@

Each link and paper survey was personalized to the restaurant's ID number. The link lead to the survey, which asked for confirmation of the last three digits of the restaurant's postal code. This was to ensure that no mailing mistakes were made, and to prevent duplicate data collection. Once verified, the survey-taker was given the main survey. The survey portion of the experiment cost $6,711.18. A detailed breakdown of costs can be found in [Appendix A](#appendixA).

@@

* Demographic information
  - Disability status: According to the UN Convention on the Rights of Persons with Disabilities, persons with disabilities are described as having "long-term physical, mental, intellectual or sensory impairments which in interaction with various barriers may hinder their full and effective participation in society on an equal basis with others."
  - Indigenous status: According to the Government of Canada, Indigenous people include "First Nations (North American Indian), Métis or Inuit and/or those who reported Registered or Treaty Indian status, that is registered under the Indian Act of Canada, and/or those who reported membership in a First Nation or Indian band". 
  - Visible minority (non-Indigenous) status: "Visible minority" is defined by the Government of Canada as "persons, other than aboriginal peoples, who are non-Caucasian in race or non-white in colour."
  - Gender identity
* Type of service provided (dine-in, take-out, or both)
* Revenue in May 2021
* Employees
  - Number of full-time employees (30 hours/week or more)
  - Number of part-time employees (less than 30 hours/week)

@@

As noted in the results from Survey 2, the intervention led to a noticeable difference in reported revenues. The mean reported revenue for the treatment group was \$45,959.60 and $70,675.60 for the control. The revenue distribution for both groups is show in Figure \@ref(fig:postrevenue). The mean number of employees, both full-time and part-time, show a were noticeably different as well. There were an average of 8.0 full-time and 4.7 part-time employees in control group restaurants, but only 5.2 full-time and 3.0 part-time employees in the treatment group restaurants. Figure \@ref(fig:postemployees) shows further detail of this finding.

>>>>

---
title: "COVID-19 Closures Impact Restaurant Revenue and Employment Unequally"
author: "Lorena Almaraz De La Garza, Amy Farrow, and Kumalasari Sondjaja"
date: "September 20th, 2021"
output:
  bookdown::pdf_document2:
    toc: yes
subtitle: "A randomized controlled trial to identify the impact of mandatory partial closures on Ontario restaurants"
abstract: "This report covers an experiment conducted by Petit Poll to test the impact of COVID-19 closures on Ontario restaurants. A randomized controlled trial was conducted and surveys were used to collect results. The data show that restaurant revenue and employee counts were negatively impacted by a mandatory two-week partial closure, and dine-in restaurants and restaurants owned by visible minorites were more negatively impacted. These results suggest that if more closures are necessary, Ontario should assist restaurant owners by offering support for take-out services and minority-owned businesses."
thanks: 'Code and data are available at: [github.com/amycfarrow/ontariorestaurantclosuresexperiment](https://github.com/amycfarrow/ontariorestaurantclosuresexperiment).'
bibliography: references.bib
---

@@

The target population for this study was all restaurants in Ontario. Because restaurant inspection is carried out by different authorities across the province, a list of Ontario local health authorities (LHAs) was collected. These LHAs were the primary sampling units, forming the primary sampling frame, or list of units of interest from which to draw a sample. Using census data from 2016, the primary sampling frame was stratified into small LHAs (population of less than 150,000), medium LHAs (population of 150,000 to 400,000), and large LHAs (population of more than 400,000). Each stratum contained the same number of LHAs. From each stratum, two LHAs were randomly sampled to participate in the treatment, and two LHAs were randomly selected to participate in the control. This primary sample is shown in Table \@ref(tab:treatmentcontrolgroups).

@@

Each link and paper survey was personalized to the restaurant's ID number. The link led to the survey, which asked for confirmation of the last three digits of the restaurant's postal code. This was to ensure that no mailing mistakes were made, and to prevent duplicate data collection. Once verified, the survey-taker was presented with the main survey. The survey portion of the experiment cost $6,711.18. A detailed breakdown of costs can be found in [Appendix A](#appendixA).

@@

* Demographic information
  - Disability status: According to the United Nations Convention on the Rights of Persons with Disabilities, persons with disabilities are described as having "long-term physical, mental, intellectual or sensory impairments which in interaction with various barriers may hinder their full and effective participation in society on an equal basis with others."
  - Indigenous status: According to the Government of Canada, Indigenous people include "First Nations (North American Indian), Métis or Inuit and/or those who reported Registered or Treaty Indian status, that is registered under the Indian Act of Canada, and/or those who reported membership in a First Nation or Indian band". 
  - Visible minority (non-Indigenous) status: "Visible minority" is defined by the Government of Canada as "persons, other than aboriginal peoples, who are non-Caucasian in race or non-white in colour."
  - Gender identity
* Type of service provided (dine-in, take-out, or both)
* Revenue in May 2021
* Employees
  - Number of full-time employees (30 hours/week or more)
  - Number of part-time employees (less than 30 hours/week)

@@

As noted in the results from Survey 2, the intervention led to a noticeable difference in reported revenues. The mean reported revenue for the treatment group was \$45,959.60 and $70,675.60 for the control. The revenue distribution for both groups is show in Figure \@ref(fig:postrevenue). The mean number of employees, both full-time and part-time, were noticeably different as well. There were an average of 8.0 full-time and 4.7 part-time employees in control group restaurants, but only 5.2 full-time and 3.0 part-time employees in the treatment group restaurants. Figure \@ref(fig:postemployees) shows further detail of this finding.
